The Overlapping Control Volume Finite Element Method for Multiphase Porous Media Flow Modelling \\ Part I: Numerical Formulation

### 2015-01-09 Papers/Prototype_1_Method/article.tex
updates

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Solving the Linear Equations}\label{Section:SolvingLinearEqns}
The global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and force balance equations (Eqn.~\ref{force-balance-matrix-form}) are solved by substituting out the force density term and solving the system of equations for pressure. At time level $n+1$, Eqns.~\ref{force-balance-matrix-form} and ~\ref{glob-cty-matrix} can be rewritten as:
\begin{displaymath}
%\label{glob-cty-matrix2},\label{force-balance-matrix-form2}
%\begin{eqnarray}
 % &&
\begin{cases}
 \mathbf{M} \underline{\bf v}^{n+1} = \mathbf{C}\underline{\bf p}^{n+1} + \underline{\bf s}_{u}^{n+1} \\ %&&
 \mathbf{B}_\sigma^{T} \underline{\bf v}^{n+1} = \underline{\bf s}_{p}^{n+1},%\label{glob-cty-matrix2}
\end{cases}
%\end{eqnarray}
\end{displaymath}
respectively. Application of a discontinuous FEM for the force density leads to a block-diagonal $\mathbf{M}_{\sigma}$ matrix that can be readily inverted, each block being local to an element. Multiplying Eqn.~\ref{force-balance-matrix-form} by $\mathbf{B}^{T}\mathbf{M}_{\sigma}^{-1}$ and summing up with Eqn.~\ref{glob-cty-matrix}, the force density $\left(\underline{\mathbf v}^{n+1}\right)$ vanishes and the pressure equation is obtained:
\begin{equation}
  \mathbf{B}_\sigma^{T}\mathbf{M}^{-1} \mathbf{C} \underline{\bf p}^{n+1} = \underline{\bf s}_{p}^{n+1} - \mathbf{B}_\sigma^{T} \mathbf{M}^{-1} \underline{\bf s}_{u}^{n+1}.
  \label{final_projection}
\end{equation}
Eqn.~\ref{final_projection} is solved for pressure and then the velocity is obtained via Eqn.~\ref{force-balance-matrix-form}. The computationally demanding effort to solve the pressure matrix equation arising from the fully discontinuous FEM formulation is achieved using a multigrid-like approach. In this case the $\lq$fine' mesh is the one obtained by the discontinuous system, whereas the $\lq$coarse' mesh is obtained by creating from the discontinuous system a continuous one by collapsing the pressure nodes. As in multigrid, the coarse mesh solution is used to accelerate the convergence of the fine mesh solution by calculating the error of the present approximation.

>>>>

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Solving the Linear Equations}\label{Section:SolvingLinearEqns}
The global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and force balance equations (Eqn.~\ref{force-balance-matrix-form}) are solved by substituting out the force density term and solving the system of equations for pressure. At time level $n+1$, Eqns.~\ref{force-balance-matrix-form} and ~\ref{glob-cty-matrix} can be rewritten as:
\begin{displaymath}
%\label{glob-cty-matrix2},\label{force-balance-matrix-form2}
%\begin{eqnarray}
 % &&
\begin{cases}
 \mathbf{M} \underline{\bf v}^{n+1} = \mathbf{C}\underline{\bf p}^{n+1} + \underline{\bf s}_{u}^{n+1} \\ %&&
 \mathbf{B}_\sigma^{T} \underline{\bf v}^{n+1} = \underline{\bf s}_{p}^{n+1},%\label{glob-cty-matrix2}
\end{cases}
%\end{eqnarray}
\end{displaymath}
respectively. Application of a discontinuous FEM for the force density leads to a block-diagonal $\mathbf{M}_{\sigma}$ matrix that can be readily inverted, each block being local to an element. Multiplying Eqn.~\ref{force-balance-matrix-form} by $\mathbf{B}^{T}\mathbf{M}_{\sigma}^{-1}$ and summing up with Eqn.~\ref{glob-cty-matrix}, the force density $\left(\underline{\mathbf v}^{n+1}\right)$ vanishes and the pressure equation is obtained:
\begin{equation}
  \mathbf{B}_\sigma^{T}\mathbf{M}^{-1} \mathbf{C} \underline{\bf p}^{n+1} = \underline{\bf s}_{p}^{n+1} - \mathbf{B}_\sigma^{T} \mathbf{M}^{-1} \underline{\bf s}_{u}^{n+1}.
  \label{final_projection}
\end{equation}
Eqn.~\ref{final_projection} is solved for pressure and then the velocity is obtained via Eqn.~\ref{force-balance-matrix-form}. The computationally demanding effort to solve the pressure matrix equation arising from the fully discontinuous FEM formulation is achieved using a multigrid-like approach. In this case the $\lq$fine' mesh is the one obtained by the discontinuous system, whereas the $\lq$coarse' mesh is obtained by creating, from the discontinuous system, a continuous system by collapsing the pressure nodes. As in multigrid, the coarse mesh solution is used to accelerate the convergence of the fine mesh solution by calculating the error of the current approximation.
